Placeholder Title

### 2020-08-22 paper/paper.tex
WIP

\documentclass{article}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage[numbers]{natbib}

\bibliographystyle{plainnat}

\title{Formatting instructions for NeurIPS 2018}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

@@

\begin{abstract}
    One of the saught after objectives within neural architecture search
    is the reduction of search time. Some recent approaches attempt to reduce
    search time by using surrogate performance metric that predict performance
    based on learning curves and/or architecture embeddings. 
    In this paper, a architecture-agnostic, surrogate-model-less approach is explored as an accelerator for
    evolutionary-strategy-based neural architeure search, experimentally achieving
    acceleration of 8x while also providing benefits to exploration of the search space.
\end{abstract}

@@

\subsection{Style}

Papers to be submitted to NeurIPS 2018 must be prepared according to the
instructions presented here. Papers may only be up to eight pages long,
including figures. Additional pages \emph{containing only acknowledgments and/or
  cited references} are allowed. Papers that exceed eight pages of content
(ignoring references) will not be reviewed, or in any other way considered for
presentation at the conference.

The margins in 2018 are the same as since 2007, which allow for $\sim$$15\%$
more words in the paper compared to earlier years.

Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
NeurIPS website as indicated below. Please make sure you use the current files
and not previous versions. Tweaking the style files may be grounds for
rejection.

\subsection{Retrieval of style files}

The style files for NeurIPS and other conference information are available on
the World Wide Web at
\begin{center}
  \url{http://www.neurips.cc/}
\end{center}
The file \verb+neurips_2018.pdf+ contains these instructions and illustrates the
various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2018 is \verb+neurips_2018.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{} 2.09,
  Microsoft Word, and RTF are no longer supported!}

The \LaTeX{} style file contains three optional arguments: \verb+final+, which
creates a camera-ready copy, \verb+preprint+, which creates a preprint for
submission to, e.g., arXiv, and \verb+nonatbib+, which will not load the
\verb+natbib+ package for you in case of package clash.

\paragraph{New preprint option for 2018}
If you wish to post a preprint of your work online, e.g., on arXiv, using the
NeurIPS style, please use the \verb+preprint+ option. This will create a
nonanonymized version of your work with the text ``Preprint. Work in progress.''
in the footer. This version may be distributed as you see fit. Please \textbf{do
  not} use the \verb+final+ option, which should \textbf{only} be used for
papers accepted to NeurIPS.

At submission time, please omit the \verb+final+ and \verb+preprint+
options. This will anonymize your submission and add line numbers to aid
review. Please do \emph{not} refer to these line numbers in your paper as they
will be removed during generation of camera-ready copies.

The file \verb+neurips_2018.tex+ may be used as a ``shell'' for writing your
paper. All you have to do is replace the author, title, abstract, and text of
the paper with your own.

The formatting instructions contained in these style files are summarized in
Sections \ref{gen_inst}, \ref{headings}, and \ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas) wide and
9~inches (54~picas) long. The left margin is 1.5~inch (9~picas).  Use 10~point
type with a vertical spacing (leading) of 11~points.  Times New Roman is the
preferred typeface throughout, and will be selected for you by default.
Paragraphs are separated by \nicefrac{1}{2}~line space (5.5 points), with no
indentation.

The paper title should be 17~point, initial caps/lower case, bold, centered
between two horizontal rules. The top rule should be 4~points thick and the
bottom rule should be 1~point thick. Allow \nicefrac{1}{4}~inch space above and
below the title to rules. All pages should start at 1~inch (6~picas) from the
top of the page.

For the final version, authors' names are set in boldface, and each name is
centered above the corresponding address. The lead author's name is to be listed
first (left-most), and the co-authors' names (if different address) are set to
follow. If there is only one co-author, list both author and co-author side by
side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

@@

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the heading in
bold, flush left, and inline with the text, with the heading followed by 1\,em
of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.  Citations may be
author/year or numeric, as long as you maintain internal consistency.  As to the
format of the references themselves, any style is acceptable as long as it is
used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations appropriate for
use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may add the
following before loading the \verb+neurips_2018+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add the optional
argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{neurips_2018}
\end{verbatim}

As submission is double blind, refer to your own published work in the third
person. That is, use ``In the previous work of Jones et al.\ [4],'' not ``In our
previous work [4].'' If you cite your other papers that are not widely available
(e.g., a journal paper under review), use anonymous author names in the
citation, e.g., an author of the form ``A.\ Anonymous.''

@@

All tables must be centered, neat, clean and legible.  The table number and
title always appear before the table.  See Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical rules.} We
strongly suggest the use of the \verb+booktabs+ package, which allows for
typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

@@

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style files.  In
particular, do not modify the width or length of the rectangle the text should
fit into, and do not change font sizes (except perhaps in the
\textbf{References} section; see below). Please note that pages should be
numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and not, for
example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file must only
contain Type 1 or Embedded TrueType fonts. Here are a few instructions to
achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader, select the
  menu Files$>$Document Properties$>$Fonts and select Show All Fonts. You can
  also use the program \verb+pdffonts+ which comes with \verb+xpdf+ and is
  available out-of-the-box on most Linux machines.

\item The IEEE has recommendations for generating PDF files whose fonts are also
  acceptable for NeurIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap fonts.  Use
  "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You should use
  the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or \verb+\mathbb{C}+
for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You can also use the following
workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the \verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we will ask
you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always specify the
figure width as a multiple of the line width as in the example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly hyphenate a
line. Please give LaTeX hyphenation hints using the \verb+\-+ command when
necessary.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All acknowledgments
go at the end of the paper. Do not include acknowledgments in the anonymized
submission, only in the final paper.

\section*{References}

References follow the acknowledgments. Use unnumbered first-level heading for
the references. Any choice of citation style is acceptable as long as you are
consistent. It is permissible to reduce the font size to \verb+small+ (9 point)
when listing the references. {\bf Remember that you can use more than eight
  pages as long as the additional pages contain \emph{only} cited references.}
\medskip

\small

@@

>>>>

\documentclass[twocolumn]{article}
\usepackage[bottom=10em,top=10em,right=5em,left=5em]{geometry}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage[numbers]{natbib}
\usepackage{pgfplots}
\usepackage{layouts}
\usepackage{placeins}
\usepackage{layout}

\bibliographystyle{plainnat}
\setlength{\headsep}{5pt}

\title{Placeholder Title}

@@

\begin{abstract}
    One of the saught after objectives within neural architecture search
    is the reduction of search time. Some recent approaches attempt to reduce
    search time by using surrogate performance metric that predict performance
    based on learning curves and/or architecture embeddings. 
    In this paper, the efficacy of purely statistical methodology for accelerating
    the search time of evolutionary algorithm oriented NAS approaches is assessed. Analysis of results
    suggests that statistical methods do not provide meaningful search time reductions
    within commonly used NAS search spaces.
\end{abstract}

@@

\subsection{Background and Related Work}

For NAS approaches utilizing genetic evolutionary algorithms, the means with which the algorithm determines the most and least fit candidates 
for mutation and optionally removal hinges upon the ability to determine comparative performance between candidates. The go-to metric for 
determining the performance of candidates with single-objective models is validation or test accuracy or error. However, recent approaches 
have forgone ratio variables to measure perforance in favor of ordinal variables \cite{pnas}, since relative performance is the only necessity 
for common selection strategies like traditional tournament selection and its variations, such as aging selection \cite{amoebanet}. 
In the case of PNAS \cite{pnas}, a surrogate model is used to predict model performance in a way that ranks models approximately as they would
be ranked as they would be using actual performance.

\subsection{Approach}

Using a surrogate model to predict model rank has the downside of training surrogate model to predict in a space that's growing in parallel with the
surrogate. PNAS \cite{pnas} proposes a clever solution to this which allows the surrogate to train over more data during the beginning of search.
Its proposed approach is only possible due to the fact that the PNAS search space has the capability to expand its search space in a way that
allows the initial, smaller search spaces to be representative of the later, larger search spaces in a way that is meaningful to the surrogate.
Such an approach doesn't provide benefits to search spaces that aren't expandable in a manner similar to that of PNAS, which means a surrogate would
have to train on architectures representing a complete search space.

Surrogate models are not the only way to predict candidate ranking. Two ways to represent relative performances of a population of candidates are the following 'performance metrics':

- Raw Rank Measurements Based on Candidate Accuracy

Rank measurements are a clear way to represent accuracies as ordinal data. No additional explanation is necessary.

- Z-Scores of Candidate Accuracy

Zz-scores of candidate performance can somewhat act as interval data and thus can better represent outliers and clusters in comparison to raw ranks. 
Z-Scores are typically used with normal distributions.
Model accuracies in NASBench 201 \cite{nasbench201} provide a complete view of the distributions of accuracies in what could be considered to be 
a search space representative of common NAS search spaces. 
An Anderson-Darling test over model test accuracies for Cifar10 (200 epochs) in NASBench201 produces a test statistic of 2717.199 
(718.514 after a Box-Cox transform) indicates at all significance levels that model accuracies do not fall into a normal distribution. 
Nonetheless, z-scores still provide a way to judge relative model performance.

The relevant benefit of ordinal and interval performance metrics is that a population's measurements evaluated at an early epoch are 
directly comparable to its measurements at a later epoch. This is the basis for the possibility of search time acceleration, since
the early performances have the potential to be predictive of final performances.

% \printinunitsof{in}\prntlen{\textwidth}

\subsection{Stochastic Search Experimentation}

\subsubsection{Experiment Details}
To measure the potential of the use of z-scores and raw ranks as a predictors of final performance, populations of models are used to
emulate a stochastic search that is accelerated by early performance prediction. 
While stochastic search is a far-from-optimal search algorithm, this experiment's goal is rather to provide insight into the reliability 
using the two performance predictors to find the best candidates at different population sizes.

Two populations of trained models from two different architecutre search spaces are sampled for this purpose.
The first population is generated using a variety of hyperparemeter combinations within a search space similar to that of NASNet \cite{nasnet}.
Implementation details of this search space are provided in the appendix. 
The second population is a sampled subset of the architectures in NASBench201 \cite{nasbench201}.

Each population $P$ is evaluated at each combination between elements of $E^s$, $W^s$, and $M$.
Each such evaluation at a given combination is referred to as a \emph{simulation}.
The set of \emph{prediction epoch scalars} $E^s$ scales $t$, the total number of epochs per model in $P$,
to produce the actual \emph{prediction epochs} at which final model performance rank will be predicted, $E^{a}$.
This facilitates early performance prediction and thus the potential for search acceleration.
The set of \emph{prediction window scalars} $W^s$ scales $E^a$ to produce the actual \emph{prediction windows} to be used 
over trained epochs to be used during evaluation, $W^a$.
The set of \emph{evaluation metric} functions $M$ includes functions for calculating an evaluation metric,
given a model, a prediction epoch, and a prediction window. 
These metric functions include averaged-over-window z-score measurements \emph{zm}'s, and raw rank measurements \emph{rm}'s.

\[E^s = \{1, 0.5, 0.25, 0.125\}\]
\[W^s = \{1, 0.5, 0.25, 0.001\}\]
\[M = \{f_{zm}, f_{rm}\}\]

\[f_{zm}(x, e, w) = \frac{1}{e-w}\sum_{i=e-w}^{e}\frac{x_i - \mu_i}{\sigma_i}\]
\[f_{rm}(x, e, w) = \frac{1}{e-w}\sum_{i=e-w}^{e}r_{x_{i}}(P)\]

\[predictions(P, e, w, f_{predictor}) = r(map(P, f_{predictor}))\]

\[r(P) = rank\ of\ every\ element\ in\ P\]
\[r_{x}(P) = rank\ of\ x\ within\ P\]

In each simulation, $P$ is shuffled then evaluated as an incremental subset of the shuffled population.
Thus, each simulation evaluates a simulated population as if it were growing to its final size, while using
the evaluation metrics to estimate simulated population rankings at each step.
This allows a direct comparison between the predicted rankings and actual rankings at each increment.
Simlar to PNAS \cite{pnas}, the Spearman Coefficient is chosen to judge the reliability of early prediction of population performance ranks.
At the addition of each subsequent model to the simulated population, average rank error, rank error for the newest model (new rank error), and the Spearman Coefficient
for the population are measured and used as evaluation metrics. 
Each simulation is run $N$ times, and evaluation metrics are averaged across simulation iterations. 
Refer to the Figure ~\ref{fig:nasnet_1x_acceleration}, ~\ref{fig:nasnet_2x_acceleration}, ~\ref{fig:nasnet_4x_acceleration}, and ~\ref{fig:nasnet_8x_acceleration} in Appendix for simulation results.
Additionally, the correlation between new models' predicted rank error and new models' predicted rank is measured for each simulation,
and results are averaged across simulation iterations. These results can be found in Figure ~\ref{fig:rank_error_correlations}.

\subsubsection{Analysis}

\textbf{Higher acceleration rates result in higher average and new rank error, and lower Spearman coefficients.}
New rank error and Spearman ccoefficients converge to levels that show clear trend that increases with acceleration rate.
This is unsurprising, as these measurements are based on model performance that are further away in terms of epochs to their
otherwise final performance. 
As acceleration rate increases, average rank error comes closer to stabilizing around $\frac{1}{3}$, the expected average error rate
for a random population, but the rank predictions causing such a rank error are clearly not random since the Spearman coefficient is far from zero.

\textbf{New rank error stabilizes at a lower value than average rank error.}
In all simulations, new rank error appears to stabilize at approximately half the value of the average rank error.
Additionally, new rank error stabilizes faster than average rank error, stabilizing near a population of 4 while
average rank error begins to stabilize around a population of 12.

\textbf{Model size appears to impact performance prediction accuracy.} 
The NASNet model population is comprised of models which all are larger than their NASBench201 counterparts.
With NASNet simulations, Spearman coefficients remain consistenly higher and new rank error levels off at a lower value in comparison to NASBench201 simulations.
Nonetheless, NASNet simulations show an average rank error trajectories similar to the trajectories that NASBench201 simulations play out.
\textbf{Where do average rank error/new rank error/spearman coeff actually level out to? - take last quarter and average it?}

\textbf{Prediction based on zscores and prediction based on raw ranks produce virtually the same results.}
This is more evident with NASBench201 since it draws out to a higher population size. 
\textbf{CORRELATION?}

\textbf{New rank error has an overall weak-to-moderate positive correlation with the predicted new rank itself.}
This trend is better observed with NASBench201 simulations, due to the fact that its larger simulated population will produce an innately more accurate
representation of such a trend. 
\textbf{HOW DOES THIS CORRELATE WITH INCREASING ACCELERATION RATE?}
This trend can be interpreted optimistically to suggest that, in an evolution context, degrees of exploration will be bolstered
outside of the exploration facilitated by the evolutionary algorithm alone. 
Pessimistically, this trend can be interpreted to suggest that suboptimal candidates might be chosen during the selection step of
evolutionary selection algorithms, resulting in slower time to find better candidates or the possibility for better candidates
to be spuriously removed.

\section{Aging Search Experimentation}

Results from stochastic search experimentation are only applicable to an evolutionary algorithm context during the population's development prior to 
selection mechanisms taking effect, since selection mechanisms generally increase the frequency of higher-performance candidates. 
With a higher concentration of highly-performaning candidates in a population, the given evaluation metrics might perform less reliably.

testtest

@@

@@

@@

@@

\FloatBarrier
\clearpage
\onecolumn
\appendix
\section{Appendix}
\subsection{Stochastic Search Results}
\subsubsection{NASNet Simulations}
\begin{figure}[!h]
    \begin{center}
        \input{../evolution/nasnet_1.0x_acceleration.pgf}
    \end{center}
    \caption{NASNet Simulation with 1x Acceleration}
    \label{fig:nasnet_1x_acceleration}
\end{figure}
\begin{figure}
    \begin{center}
        \input{../evolution/nasnet_2.0x_acceleration.pgf}
    \end{center}
    \caption{NASNet Simulation with 2x Acceleration}
    \label{fig:nasnet_2x_acceleration}
\end{figure}

\begin{figure}
    \begin{center}
        \input{../evolution/nasnet_4.0x_acceleration.pgf}
    \end{center}
    \caption{NASNet Simulation with 4x Acceleration}
    \label{fig:nasnet_4x_acceleration}
\end{figure}

\begin{figure}
    \begin{center}
        \input{../evolution/nasnet_8.0x_acceleration.pgf}
    \end{center}
    \caption{NASNet Simulation with 8x Acceleration}
    \label{fig:nasnet_8x_acceleration}
\end{figure}

\begin{figure}
    \begin{center}
        \input{../evolution/nasnet_rank_error_correlations.pgf}
    \end{center}
    \caption{NASNet Rank Error Correlations with Rank}
    \label{fig:nasnet_rank_error_correlations}
\end{figure}

\FloatBarrier
\clearpage
\subsubsection{NASBench201 Simulations}

\begin{figure}[!h]
    \begin{center}
        \input{../evolution/nasbench_16_1.0x_acceleration.pgf}
    \end{center}
    \caption{NASBench201 Simulation with 1x Acceleration}
    \label{fig:nasbench_1x_acceleration}
\end{figure}

\begin{figure}
    \begin{center}
        \input{../evolution/nasbench_16_2.0x_acceleration.pgf}
    \end{center}
    \caption{NASBench201 Simulation with 2x Acceleration}
    \label{fig:nasbench_2x_acceleration}
\end{figure}

\begin{figure}
    \begin{center}
        \input{../evolution/nasbench_16_4.0x_acceleration.pgf}
    \end{center}
    \caption{NASBench201 Simulation with 4x Acceleration}
    \label{fig:nasbench_4x_acceleration}
\end{figure}

\begin{figure}
    \begin{center}
        \input{../evolution/nasbench_16_8.0x_acceleration.pgf}
    \end{center}
    \caption{NASBench201 Simulation with 8x Acceleration}
    \label{fig:nasbench_8x_acceleration}
\end{figure}

\begin{figure}
    \begin{center}
        \input{../evolution/nasbench_16_rank_error_correlations.pgf}
    \end{center}
    \caption{NASBench201 Rank Error Correlations with Rank}
    \label{fig:nasbench_rank_error_correlations}
\end{figure}

\FloatBarrier
\clearpage
\subsection{NASNet Population Details}

Using these possible ops

Each evaluated to 16 epochs, how big is population?

hyperparameters are as follows.

UPDATE CHARTS TO INDICATE WHAT ORANGE/BLUE MEANS
